---
title: "Comparing Precovid and Y1.5 Data"
date: "8/12/2020"
output: html_document
---

```{r include=FALSE}
#neccesary libraries 

library(readr)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(readxl)
library(car)
library(kimisc)
library(checkmate)
library(Hmisc)
```

### Goal
Compare Y1.5 mhw screens (during Covid) vs Y1 screens (preCovid) for significant differences

### Data
152 students from 8 different colleges, Daytona, Prescott, Iowa, SDSU, SJSU, Cal Poly, Milwaukee, and Boulder, responded to the survey both before Covid and during Covid. Therefore, we are able to conduct 2-sample tests for equality of proportions, which is used to compare two proportions from two different groups to see if there is a significant difference between the proportion of students who had a positive screen from each group (precovid and during covid). It is important to note we need to use proportions since some students did not answer certain questions, and the sample size is different for each screen we look at.  

```{r warning=FALSE, include=FALSE}
#reading in the y1.5 data from each school

Daytona <- read_excel("ERAU Daytona COVID-19 Collection Characterizing Engineering Student Me.xlsx")

Prescott <- read_excel("ERAU Prescott COVID-19 Collection Characterizing Engineering Student M.xlsx")

Iowa <- read_excel("Iowa State COVID 19 Collection Characterizing Engineering Student Ment.xlsx")

SDSU <- read_excel("SDSU COVID-19 Collection Characterizing Engineering Student Mental Wel.xlsx")

SJSU <- read_excel("SJSU COVID-19 Collection Characterizing Engineering Student Mental Wel.xlsx")

CPSU <- read_excel("Cal Poly Characterizing Engineering Student Mental Wellness and Its Role i.xlsx")

Milwaukee <- read_excel("UW Milwaukee COVID 19 Collection Characterizing Engineering Student Me (1).xlsx") 

Boulder <- read_excel("CU Boulder COVID-19 Collection Characterizing Engineering Student Ment (1).xlsx")
```

```{r include=FALSE}
#combine the y1.5 data sets from each school

dataset <- rbind(Daytona, Prescott,Iowa,SDSU,SJSU,CPSU,Milwaukee,Boulder)
```

```{r include=FALSE}
#take out those who declined to participate 

data <- dataset[-c(91,101,159,179),]
```

```{r include=FALSE}
#parse_funcs.r

parse.var.yes_no <- data.frame(likert = c("Yes", "No"),
                     value=c(1,0),stringsAsFactors=FALSE)

parse.var.not_sev_mohalf_ned <- data.frame(likert = c("Not at all", "Several days",
                                    "More than half the days",
                                    "Nearly every day"),
                                    value=c(0,0,1,1),stringsAsFactors=FALSE)

parse.var.not_sev_mohalf <- data.frame(likert = c("Not at all", "Several Days",
                                                      "More than half the days"),
                                           value=c(0,0,1),stringsAsFactors=FALSE)

parse.pcptsd <- function(data){
    lmap <- parse.var.yes_no
    
    pcptsd_headers <- grep("pcptsd", names(data), value=TRUE)
    
    data <- parse.likert(data=data, header_names=pcptsd_headers, likert_map=lmap)
    
    return(data)
}
parse.phq.eating <- function(data){
    lmap <- parse.var.yes_no
    
    eating_headers <- c(grep("phq_6", names(data),value=TRUE),grep("phq_7", names(data),value=TRUE),grep("phq_8", names(data),value=TRUE))
    
    data <- parse.likert(data=data, header_names=eating_headers, likert_map = lmap)
    
    return(data)
}
parse.phq.other_anx <- function(data){
    lmap <- parse.var.not_sev_mohalf
    
    other_headers <- grep("phq_5", names(data),value=TRUE)
    
    data <- parse.likert(data=data, header_names = other_headers, likert_map = lmap)
    
    return(data)
}
parse.phq.panic <- function(data){
    
    yes_no <- parse.var.yes_no
    panic_headers <- c(grep("phq_3", names(data),value=TRUE), grep("phq_4", names(data),value=TRUE))
    
    data <- parse.likert(data=data,header_names=panic_headers, likert_map=yes_no)
    
    return(data)
}
parse.phq.dep <- function(data){
    atoh_score <- parse.var.not_sev_mohalf_ned
    
    i_score <- data.frame(likert = c("Not at all", "Several Days",
                                        "More than half the days",
                                        "Nearly every day"),
                          value=c(0,1,1,1),stringsAsFactors=FALSE)

    dep_headers <- grep("phq_2", names(data),value=TRUE)
    
    data <- parse.likert(data=data, header_names=dep_headers[1:8],
                         likert_map=atoh_score)
    data <- parse.likert(data=data, header_names=dep_headers[9],
                         likert_map=i_score)
    
    return(data)
}
parse.kessler <- function(data){

    kesscore <- data.frame(likert = c("All of the time","Most of the time","Some of the time","A little of the time","None of the time"), value=c(4,3,2,1,0),stringsAsFactors = FALSE)
    #Grab the kessler 6 headings
    kessler_headers <- kessnames <- grep("_", grep("kessler", names(data), value=TRUE), invert = TRUE, value = TRUE)

    #Copy the relevant kesler rows for manipulation
    #kesslerdata <- data[kessler_headers]

    data <- parse.likert(data=data, header_names=kessler_headers,
                         likert_map=kesscore)

    return(data)
}

parse.likert <- function(data, header_names, likert_map){
    likertdata <- data[header_names]
    
    data[header_names] <- likertdata %>%
        pivot_longer(cols = header_names,names_to = "lscale",
                     values_to="likert") %>%
        left_join(likert_map, by = "likert") %>%
        mutate(likert=value) %>%
        select(-value) %>%
        pivot_wider(names_from = "lscale", values_from="likert",
                    values_fn = list(likert = list)) %>%
        unnest(cols=header_names)
    return(data)
}
```

```{r include=FALSE}
#Kessler Analysis

analysis.kessler <- function(data){
    data<-parse.kessler(data)
    #add for major mental health
    data <- mutate(data,
                   kessler_major =
                       ifelse((coalesce.na(kessler1,0)+coalesce.na(kessler2,0)+coalesce.na(kessler3,0)+coalesce.na(kessler4,0)+coalesce.na(kessler5,0)+
                                coalesce.na(kessler6,0))>=13, 1,
                               ifelse((coalesce.na(kessler1,4)+coalesce.na(kessler2,4)+coalesce.na(kessler3,4)+coalesce.na(kessler4,4)+coalesce.na(kessler5,4)+
                                coalesce.na(kessler6,4)) < 13, 0, NA))
                   )
    data <- mutate(data,
                   kessler_moderate =
                     ifelse(kessler_major, 0, 
                       ifelse((coalesce.na(kessler1,0)+coalesce.na(kessler2,0)+coalesce.na(kessler3,0)+coalesce.na(kessler4,0)+coalesce.na(kessler5,0)+
                                coalesce.na(kessler6,0))>=5 & !coalesce.na(kessler_major, TRUE), 1 , ifelse((coalesce.na(kessler1,4)+coalesce.na(kessler2,4)+coalesce.na(kessler3,4)+coalesce.na(kessler4,4)+coalesce.na(kessler5,4)+
                                coalesce.na(kessler6,4)) < 5, 0, NA)
                              )
                       )
                   )
    return(data)
}

data = analysis.kessler(data)
```

```{r include=FALSE}
# phq analysis 

analysis.phq.depr <- function(data){
                                        #Grab phq_2a-2i
    dep_headers <- grep("phq_2", names(data),value=TRUE)
    #Parse the data to replace Likert style scores with 1s if they count and 0s
    #if they don't
    data <- parse.phq.dep(data)
    data <- mutate(data,
                      dep_major = ifelse(
                      (rowSums(coalesce.na(data[dep_headers[-1:-2]],0))>=5) &
                       (rowSums(coalesce.na(data[dep_headers[1:2]],0))>=1), 1,
                      ifelse(rowSums(is.na(data[dep_headers[1:2]])) >= 1 & (rowSums(data[dep_headers[-1:-2]], na.rm = T) + rowSums(is.na(data[dep_headers[-1:-2]]))) >=5, NA, 0)
                   ))
                   #if_else(
                    #   rowSums(is.na(data[dep_headers[-1:-2]]))>=2 |
                     #      rowSums(is.na(data[dep_headers[1:2]]))==2, NA, 0))
    data <- mutate(data,
                      dep_other = ifelse(dep_major!=1, ifelse(
                      (rowSums(coalesce.na(data[dep_headers[-1:-2]], 0))>=2) &
                       (rowSums(coalesce.na(data[dep_headers[1:2]],0))>=1), 1 ,
                       ifelse(rowSums(is.na(data[dep_headers[1:2]])) >= 1 & (rowSums(data[dep_headers[-1:-2]], na.rm = T) + rowSums(is.na(data[dep_headers[-1:-2]]))) >=2, NA, 0)), 0
                   ))
    
    return(data)
}
analysis.phq.panic <- function(data){
    data <- parse.phq.panic(data)
    
    panic3_headers <- grep("phq_3", names(data),value=TRUE)
    panic4_headers <- grep("phq_4", names(data),value=TRUE)
    data <- data %>% mutate(
        panic = ifelse(rowSums(coalesce.na(data[panic3_headers],0))==4 & (rowSums(coalesce.na(data[panic4_headers],0))>=4), 1, 
                       ifelse(rowSums(is.na(data[panic3_headers]))==0, 0, ifelse((rowSums(data[panic4_headers], na.rm = T) + rowSums(is.na(data[panic4_headers]))) >=4,NA, 0)))
    )
    
    return(data)
}
analysis.phq.other <- function(data){
    data <- parse.phq.other_anx(data)
    other_headers <- grep("phq_5", names(data),value=TRUE)
    data <- data %>% mutate(
        other_anxiety = ifelse(data[other_headers[1]] & rowSums(data[other_headers[-1]], na.rm = T)>=3, 1, 
                                ifelse(rowSums(is.na(data[other_headers[1]])) == 0, 0, ifelse((rowSums(data[other_headers], na.rm = T) + rowSums(is.na(data[other_headers]))), NA, 0)))
    )
    
    return(data)
}
analysis.phq.eating <- function(data){
    data <- parse.phq.eating(data)
    eating6_headers <- grep("phq_6", names(data), value=TRUE)
    
    data <- data %>% mutate(
        bulimia = if_else(phq_8 & (rowSums(data[eating6_headers], na.rm = T)==3),1,0)
    )
    
    data <- data %>% mutate(
        bin_eat = ifelse((is.na(phq_8)|phq_8==0)& (rowSums(data[eating6_headers], na.rm = T)==3),1,
                          ifelse((is.na(phq_8)|phq_8==0)& (rowSums(data[eating6_headers], na.rm = T) + rowSums(is.na(data[eating6_headers][1:3]))) >= 3, NA, 0)
    ))
}

data <- analysis.phq.depr(data)
data <- analysis.phq.panic(data)
data <- analysis.phq.other(data)
data <- analysis.phq.eating(data)
```

```{r include=FALSE}
#PCPTSD Analysis

analysis.pcptsd <- function(data){
    data <- parse.pcptsd(data)
    ptsd_headers <- grep("pcptsd", names(data), value=TRUE)
    print(head(data[grep("pcptsd", names(data), value=TRUE)]))
    print(colnames(data))
    data <- data %>% mutate(ptsd = ifelse(rowSums(data[ptsd_headers], na.rm = T)>=3,1,
                                           ifelse(rowSums(data[ptsd_headers], na.rm = T) + rowSums(is.na(data[ptsd_headers])) >=3, NA, 0)))
}

data = analysis.pcptsd(data)

mhw.results.summarize <- function(data){
  race_gender <- with(data, aggregate(list(kessler_major=kessler_major, kessler_moderate=kessler_moderate, dep_major=dep_major, dep_other=dep_other, panic=panic, other_anxiety=other_anxiety,bulimia=bulimia,bin_eat=bin_eat,ptsd=ptsd),list(race=race, gender=gender), mean, na.rm=TRUE))
  race_gender_filtered<-filter_all(.tbl=race_gender,.vars_predicate=all_vars(!is.nan(.) & .!=1))
  #write.csv(x=cp_race_gender_filtered, file="~/mhw_analysis/calpoly_data/cp_race_gender.csv", row.names=FALSE)
  gender_sex <- with(data, aggregate(list(kessler_major=kessler_major, kessler_moderate=kessler_moderate, dep_major=dep_major, dep_other=dep_other, panic=panic, other_anxiety=other_anxiety,bulimia=bulimia,bin_eat=bin_eat,ptsd=ptsd),list(gender=gender, sexuality=sexuality), mean, na.rm=TRUE))
  gender_sex_filtered <- filter_all(.tbl=gender_sex,.vars_predicate=all_vars(!is.nan(.) & .!=1))
  #write.csv(x=cp_gender_sex_filtered, file="~/mhw_analysis/calpoly_data/cp_gender_sex.csv", row.names=FALSE)
  
  return(list(rg=race_gender, rgf=race_gender_filtered, gs=gender_sex, gsf=gender_sex_filtered))
}

```

```{r include=FALSE}
#refine the y1.5 data 

data <- data %>%
  select(`Respondent ID`, major, belief_in_grad, college, kessler_major, kessler_moderate, dep_major, dep_other, panic, other_anxiety, bulimia, bin_eat, ptsd)
```

```{r include=FALSE}
#read in the precovid data 

precovid <- read_excel("precovid.xls")
```

```{r include=FALSE}
#only use respondents shown in both the precovid and y1.5 data 

precovid <- precovid %>%
filter(uid %in% c("11347132420",
"11347686789","11347571718","11392090397","11347312441","11347731596","11347129947","11347312098","11347142768","11347446287","11389519287","11347479209","11390329043","11391656092","11151592764","11144281287","11346780684","11147866030","11144311784","11336621732","11150066463","11154936258","11144357685","11142327584","11142321442","11142203900","11006064565","11142274793","11142224278","11142204398","11145131424","11005926956","11142334739","11005927827","11005938728","11142317048","11142229508","11145665427","11143045638","11142361586","11142400813","11154613621","11142513921","11142204793","11142549584","11143150591","11005948349","11142635873","11144849850","11142302163","11145850025","11006125266","11142235074","11389525562","11390097857","11342682467","11389435057","11342707442","11389770639","11342513496","11342611487","11342635460","11391437759","11342552029","11342734561","11342746268","11389813179","11342518123","11342533557","11374529094","11379877298","11373784945","11373955939","11374137315","11373822986","11374845245","11374077685","11380076885","11373866144","11373774516","11377581043","11373785482","11373787470","11374275782","11373775014","11374545317","11373993141","11373784019","11167062587","11167046638","11168883064","11167104519","11174258690","11169103504","11167246027","11169327838","11167348229","11167310693","11167868517","11167051190","11168024264","11167388137","11179455241","11167109542","11167651366","11167513285","11170988697","11167069375","11167058316","11167337872","11173437223","11167183612","11167174668","11167614081","11167328037","11167453881","11168048683","11169392240","11167050254","11167198900","11167053507","11168878892","11167267708","11184992602","11169083460","11167187858","11167782504","11167389779","11189351635","11167115248","11170269088","11167093764","11167771560","11167190267","11167425509","11167052944","11169048310","11329125016","11329172064","11329323249","11338498362","11329090090","11329245699","11331152623","11329441539","11352183835","11141710238","11010477608","11010446878","11010783285","11141588550","11389519585"))
```

```{r include=FALSE}
#only use respondents shown in both the precovid and y1.5 data 

data <- data %>%
  filter(`Respondent ID` %in% c("11558200986","11556747583","11556136322","11554429093","11553973829","11553169854","11552880872","11552863024","11552829555","11552679460","11552455687","11552271808","11552261571","11552257124","11609881751","11602745854","11554273921","11554269180","11552920148","11552676211","11552408932","11552309463","11552304571","11623860980","11610879329","11610608032","11602946693","11602719010","11602417348","11602363671","11588116117","11556310802","11552206435","11552200959","11552169765","11551990366","11551975649","11551951190","11551946112","11551887078","11551883582","11551868822","11551865917","11551848815","11551810123","11551800943","11551765058","11551741186","11551711236","11551693258","11551615680","11551607468","11551597922","11557935873","11556593353","11556188511","11555255426","11554124184","11553302599","11553170206","11552512400","11552462985","11552374876","11552252733","11552238525","11552233241","11552232420","11552197933","11552191059","11552178728","11616938782","11610101381","11608743955","11607912124","11607017109","11602562506","11602244047","11592552426","11559155017","11554177882","11552734113","11552531058","11552415190","11552366756","11552347608","11552338930","11552300485","11552291412","11552273421","11608499239","11605988910","11605724602","11603876006","11603829640","11603287464","11603286578","11602582808","11602559251","11602516442","11602507568","11602498373","11602483490","11602455014","11602428599","11602426630","11602416120","11602415502","11602414403","11552478929","11548200352","11547820418","11546620885","11546467574","11546412255","11546340659","11546253129","11546162895","11545895376","11545737238","11544680563","11544660640","11544594246","11544561430","11544512560","11544510770","11544459425","11544321111","11544297619","11544249265","11544228709","11544176313","11544147648","11544142064","11544125870","11544121629","11544106677","11544091705","11544089959","11606184695","11604112921","11554304691","11552907968","11552731949","11552702726","11552522766","11552266019","11552242637","11602436769","11602423874","11549618751","11548726576","11548329853"))

```

### Major Psychological Distress
***1 for a positive screen for major psychological distress from Kessler instrument***

#### Y1.5 Data
```{r echo=FALSE}
#Kessler Major 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size 
kessler_major_data <- data %>%
  select(kessler_major)%>%
  filter(kessler_major %in% c("1","0"))
kessler_major_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(kessler_major == "1"),
            `n Negative Screen` = sum(kessler_major == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
kessler_major_precovid <- precovid %>%
  select(kessler_major)%>%
filter(kessler_major %in% c("1","0"))
kessler_major_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(kessler_major == "1"),
            `n Negative Screen` = sum(kessler_major == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

#2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(54,48), n=c(139,151), alternative = "two.sided", correct = FALSE)
```

During Covid has a slightly higher proportion of students screening as positive for major psychological distress from Kessler instrument. With a high p-value of 0.21 the proportions are not statistically different.

### Moderate Psychological Distress
***1 for a positive screen for moderate psychological distress (must also screen negative for Kessler major)***

#### Y1.5 Data
```{r echo=FALSE}
#Kessler Moderate 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size 
kessler_moderate_data <- data %>%
  select(kessler_moderate)%>%
  filter(kessler_moderate %in% c("1","0"))
kessler_moderate_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(kessler_moderate == "1"),
            `n Negative Screen` = sum(kessler_moderate == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
kessler_moderate_precovid <- precovid %>%
  select(kessler_moderate)%>%
filter(kessler_moderate %in% c("1","0"))
kessler_moderate_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(kessler_moderate == "1"),
            `n Negative Screen` = sum(kessler_moderate == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(61,85), n=c(139,151), alternative = "two.sided", correct = FALSE)
```

Precovid has a higher proportion of students screening as positive for moderate psychological distress from Kessler instrument. With a small p-value of 0.03 the proportions are statistically different.

### Depressive Disorder
***1 for a positive screen for major depressive disorder***

#### Y1.5 Data
```{r echo=FALSE}
#Dep Major 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
dep_major_data <- data %>%
  select(dep_major)%>%
  filter(dep_major %in% c("1","0"))
dep_major_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(dep_major == "1"),
            `n Negative Screen` = sum(dep_major == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
dep_major_precovid <- precovid %>%
  select(dep_major)%>%
filter(dep_major %in% c("1","0"))
dep_major_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(dep_major == "1"),
            `n Negative Screen` = sum(dep_major == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(20,10), n=c(137,128), alternative = "two.sided", correct = FALSE)
```

During Covid has a higher proportion of students screening as positive for depressive disorder. With a large p-value of 0.08 the proportions are not statistically different.

### Other Depressive Disorder
***1 for a positive screen for other depressive disorder (must also screen negative for dep_major)***

#### Y1.5 Data
```{r echo=FALSE}
#Dep Other 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
dep_other_data <- data %>%
  select(dep_other)%>%
  filter(dep_other %in% c("1","0"))
dep_other_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(dep_other == "1"),
            `n Negative Screen` = sum(dep_other == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
dep_other_precovid <- precovid %>%
  select(dep_other)%>%
filter(dep_other %in% c("1","0"))
dep_other_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(dep_other == "1"),
            `n Negative Screen` = sum(dep_other == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(37,13), n=c(137,128), alternative = "two.sided", correct = FALSE)
```

During Covid has a higher proportion of students screening as positive for other depressive disorders. With a very small p-value of 0.00046 the proportions are statistically different.

### Panic Disorder
***1 for a positive screen for panic disorder***

#### Y1.5 Data
```{r echo=FALSE}
#Panic 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
panic_data <- data %>%
  select(panic)%>%
  filter(panic %in% c("1","0"))
panic_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(panic == "1"),
            `n Negative Screen` = sum(panic == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
panic_precovid <- precovid %>%
  select(panic)%>%
filter(panic %in% c("1","0"))
panic_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(panic == "1"),
            `n Negative Screen` = sum(panic == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(14,19), n=c(126,141), alternative = "two.sided", correct = FALSE)
```

Precovid has a higher proportion of students screening as positive for panic disorder. With a large p-value of 0.58 the proportions are not statistically different.

### Other Anxiety Disorder
***1 for a positive screen for other anxiety disorder (respondent can screen positive for both panic and dep_other)***

#### Y1.5 Data
```{r echo=FALSE}
#Other Anxiety 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
other_anxiety_data <- data %>%
  select(other_anxiety)%>%
  filter(other_anxiety %in% c("1","0"))
other_anxiety_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(other_anxiety == "1"),
            `n Negative Screen` = sum(other_anxiety == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
other_anxiety_precovid <- precovid %>%
  select(other_anxiety)%>%
filter(other_anxiety %in% c("1","0"))
other_anxiety_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(other_anxiety == "1"),
            `n Negative Screen` = sum(other_anxiety == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(35,28), n=c(137,148), alternative = "two.sided", correct = FALSE)
```

During Covid has a higher proportion of students screening as positive for other anxiety disorders. With a large p-value of 0.178 the proportions are not statistically different.

### Bulimia
***1 for a positive screen for bulimia***

#### Y1.5 Data
```{r echo=FALSE, warning=FALSE}
#Bulimia 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
bulimia_data <- data %>%
  select(bulimia)%>%
  filter(bulimia %in% c("1","0"))
bulimia_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(bulimia == "1"),
            `n Negative Screen` = sum(bulimia == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE, warning=FALSE}
#Proportion of positive and negative screen for precovid data 
bulimia_precovid <- precovid %>%
  select(bulimia)%>%
filter(bulimia %in% c("1","0"))
bulimia_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(bulimia == "1"),
            `n Negative Screen` = sum(bulimia == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(8,1), n=c(151,146), alternative = "two.sided", correct = FALSE)
```

During Covid has a higher proportion of students screening as positive for Bulimia. With a small p-value of 0.02 the proportions are statistically different.

### Binary Eating Disorder
***1 for a positive screen for binary eating disorder (mutually exclusive with bulimia screen)***

#### Y1.5 Data
```{r echo=FALSE, warning=FALSE}
#Bin Eat 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
bin_eat_data <- data %>%
  select(bin_eat)%>%
  filter(bin_eat %in% c("1","0"))
bin_eat_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(bin_eat == "1"),
            `n Negative Screen` = sum(bin_eat == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE, warning=FALSE}
#Proportion of positive and negative screen for precovid data 
bin_eat_precovid <- precovid %>%
  select(bin_eat)%>%
filter(bin_eat %in% c("1","0"))
bin_eat_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(bin_eat == "1"),
            `n Negative Screen` = sum(bin_eat == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(5,5), n=c(137,145), alternative = "two.sided", correct = FALSE)
```

During Covid has a slightly higher proportion of students screening as positive for binary eating disorder. With a large p-value of 0.93 the proportions are not statistically different.

### PTSD
***1 for a positive screen for PTSD on the pc-ptsd scale***

#### Y1.5 Data
```{r echo=FALSE}
#PTSD 

#Proportion of positive and negative screen for y1.5 data 
#Need to do proportions because since some respondents did not answer, the two data sets (y1.5 and precovid) have a different sample size
ptsd_data <- data %>%
  select(ptsd)%>%
  filter(ptsd %in% c("1","0"))
ptsd_data %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(ptsd == "1"),
            `n Negative Screen` = sum(ptsd == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))
```

#### Precovid Data
```{r echo=FALSE}
#Proportion of positive and negative screen for precovid data 
ptsd_precovid <- precovid %>%
  select(ptsd)%>%
filter(ptsd %in% c("1","0"))
ptsd_precovid %>% 
  summarise(`Total n` = n(), 
            `n Positive Screen` = sum(ptsd == "1"),
            `n Negative Screen` = sum(ptsd == "0"),
            `Proportion Positive Screen` = round(`n Positive Screen` / `Total n`, 3),
            `Proportion Negative Screen` = round(`n Negative Screen` / `Total n`, 3)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered"))

## 2-Sample Test for Equality of Proportions
#This test is used to compare two proportions from two different groups(precovid and Y1.5) to see if there is a significant difference between the proportion of students who had a positive screen from each group.
prop.test(x=c(37,25), n=c(135,145), alternative = "two.sided", correct = FALSE)
```

During Covid has a higher proportion of students screening as positive for PTSD. With a small p-value of 0.041 the proportions are statistically different.












