---
title: "Covid Data Pipeline"
author: "Daniel DeFoe"
date: "7/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This notebook refactors the code from the rfunc folder.
```{r}
source("parse_funcs.r")
library(tidyverse)
library(kimisc)
```


## Simulate "load_raw.r"
** Note: We could use multilineheader.r if we really need** 
Questions
- I'm not sure what "sports team question" it refers to getting rid of, or it it exists in the covid data
- Do we need responedants to have started kessler for this ?
```{r}
load.raw <- function(path){
    #grab the data file and delete SurveyMonkey extra columns
    data <- read.csv(path, header = FALSE, skip=2)
    #remove sports team question if present
    #if(ncol(data)==89)
    #    data[c(31)] <- list(NULL)
    data[1] <- list(NULL)
    data[c(7:14)] <- list(NULL)

    #grab the headers
    headpath <- file.path("../table_struct/covid_data_headers.csv")
    headers <- read.csv(headpath)
    base::names(data) <- base::names(headers)
    print(head(data))
    #Check to ensure that they have a correct year in the program, consented to the survey, and at least started Kessler
    data_cleaned<-subset(data,(consent=="Yes, I volunteer, am 18 or older, and am enrolled in an undergraduate engineering program") & (access_to_instruction_course_materials_situation!=""))#& ((year_in_program == "1") | (year_in_program == "2") | (year_in_program=="Prefer not to respond")) & kessler1!="")
    names(data_cleaned)[names(data_cleaned) == "public_private.1"] = "profit_nonprofit"
    return(data_cleaned)
}

trim <- function (x) gsub("^\\s+|\\s+$", "", x)
    
```


```{r}
setwd("~/mhw_analysis/mhw_analysis")
data = load.raw("covid_data_final.csv")
data$public_private = trim(data$public_private)
```


Our qualifiers let us come out with 867 observations


## Kessler Analysis
Questions:
-how do we want to deal with the missing data
```{r}
analysis.kessler <- function(data){
    data<-parse.kessler(data)

    #add for major mental health
    data <- mutate(data,
                   kessler_major =
                       ifelse((coalesce.na(kessler1,0)+coalesce.na(kessler2,0)+coalesce.na(kessler3,0)+coalesce.na(kessler4,0)+coalesce.na(kessler5,0)+
                                coalesce.na(kessler6,0))>=13, 1,
                               ifelse((coalesce.na(kessler1,4)+coalesce.na(kessler2,4)+coalesce.na(kessler3,4)+coalesce.na(kessler4,4)+coalesce.na(kessler5,4)+
                                coalesce.na(kessler6,4)) < 13, 0, NA))
                   )
    data <- mutate(data,
                   kessler_moderate =
                     ifelse(kessler_major, 0, 
                       ifelse((coalesce.na(kessler1,0)+coalesce.na(kessler2,0)+coalesce.na(kessler3,0)+coalesce.na(kessler4,0)+coalesce.na(kessler5,0)+
                                coalesce.na(kessler6,0))>=5 & !coalesce.na(kessler_major, TRUE), 1 , ifelse((coalesce.na(kessler1,4)+coalesce.na(kessler2,4)+coalesce.na(kessler3,4)+coalesce.na(kessler4,4)+coalesce.na(kessler5,4)+
                                coalesce.na(kessler6,4)) < 5, 0, NA)
                              )
                       )
                   )

    return(data)
}

```




```{r}
data = analysis.kessler(data)
```





## PHQ Analysis
-NEED TO SET A NUMBER OF NA's which will be 
```{r}
analysis.phq.depr <- function(data){

                                        #Grab phq_2a-2i
    dep_headers <- grep("phq_2", names(data),value=TRUE)

    #Parse the data to replace Likert style scores with 1s if they count and 0s
    #if they don't
    data <- parse.phq.dep(data)

    data <- mutate(data,
                      dep_major = ifelse(
                      (rowSums(coalesce.na(data[dep_headers[-1:-2]],0))>=5) &
                       (rowSums(coalesce.na(data[dep_headers[1:2]],0))>=1), 1,
                      ifelse(rowSums(is.na(data[dep_headers[1:2]])) >= 1 & (rowSums(data[dep_headers[-1:-2]], na.rm = T) + rowSums(is.na(data[dep_headers[-1:-2]]))) >=5, NA, 0)
                   ))

                   #if_else(
                    #   rowSums(is.na(data[dep_headers[-1:-2]]))>=2 |
                     #      rowSums(is.na(data[dep_headers[1:2]]))==2, NA, 0))
    data <- mutate(data,
                      dep_other = ifelse(dep_major!=1, ifelse(
                      (rowSums(coalesce.na(data[dep_headers[-1:-2]], 0))>=2) &
                       (rowSums(coalesce.na(data[dep_headers[1:2]],0))>=1), 1 ,
                       ifelse(rowSums(is.na(data[dep_headers[1:2]])) >= 1 & (rowSums(data[dep_headers[-1:-2]], na.rm = T) + rowSums(is.na(data[dep_headers[-1:-2]]))) >=2, NA, 0)), 0
                   ))
    
    return(data)
}

analysis.phq.panic <- function(data){
    data <- parse.phq.panic(data)
    
    panic3_headers <- grep("phq_3", names(data),value=TRUE)
    panic4_headers <- grep("phq_4", names(data),value=TRUE)

    data <- data %>% mutate(
        panic = ifelse(rowSums(coalesce.na(data[panic3_headers],0))==4 & (rowSums(coalesce.na(data[panic4_headers],0))>=4), 1, 
                       ifelse(rowSums(is.na(data[panic3_headers]))==0, 0, ifelse((rowSums(data[panic4_headers], na.rm = T) + rowSums(is.na(data[panic4_headers]))) >=4,NA, 0)))
    )
    
    return(data)
}

analysis.phq.other <- function(data){
    data <- parse.phq.other_anx(data)
    other_headers <- grep("phq_5", names(data),value=TRUE)
    data <- data %>% mutate(
        other_anxiety = ifelse(data[other_headers[1]] & rowSums(data[other_headers[-1]], na.rm = T)>=3, 1, 
                                ifelse(rowSums(is.na(data[other_headers[1]])) == 0, 0, ifelse((rowSums(data[other_headers], na.rm = T) + rowSums(is.na(data[other_headers]))), NA, 0)))
    )
    
    return(data)
}

analysis.phq.eating <- function(data){
    data <- parse.phq.eating(data)
    eating6_headers <- grep("phq_6", names(data), value=TRUE)
    
    data <- data %>% mutate(
        bulimia = if_else(phq_8 & (rowSums(data[eating6_headers], na.rm = T)==3),1,0)
    )
    
    data <- data %>% mutate(
        bin_eat = ifelse((is.na(phq_8)|phq_8==0)& (rowSums(data[eating6_headers], na.rm = T)==3),1,
                          ifelse((is.na(phq_8)|phq_8==0)& (rowSums(data[eating6_headers], na.rm = T) + rowSums(is.na(data[eating6_headers][1:3]))) >= 3, NA, 0)
    ))
}
```


```{r}
data <- analysis.phq.depr(data)
data <- analysis.phq.panic(data)
data <- analysis.phq.other(data)
data <- analysis.phq.eating(data)
```








## PCPTSD Analyasis
```{r}
analysis.pcptsd <- function(data){
    data <- parse.pcptsd(data)
    ptsd_headers <- grep("pcptsd", names(data), value=TRUE)
    print(head(data[grep("pcptsd", names(data), value=TRUE)]))
    print(colnames(data))
    data <- data %>% mutate(ptsd = ifelse(rowSums(data[ptsd_headers], na.rm = T)>=3,1,
                                           ifelse(rowSums(data[ptsd_headers], na.rm = T) + rowSums(is.na(data[ptsd_headers])) >=3, NA, 0)))
    
}
```

```{r}
data = analysis.pcptsd(data)
```







```{r}
mhw.results.summarize <- function(data){
  race_gender <- with(data, aggregate(list(kessler_major=kessler_major, kessler_moderate=kessler_moderate, dep_major=dep_major, dep_other=dep_other, panic=panic, other_anxiety=other_anxiety,bulimia=bulimia,bin_eat=bin_eat,ptsd=ptsd),list(race=race, gender=gender), mean, na.rm=TRUE))

  race_gender_filtered<-filter_all(.tbl=race_gender,.vars_predicate=all_vars(!is.nan(.) & .!=1))

  #write.csv(x=cp_race_gender_filtered, file="~/mhw_analysis/calpoly_data/cp_race_gender.csv", row.names=FALSE)

  gender_sex <- with(data, aggregate(list(kessler_major=kessler_major, kessler_moderate=kessler_moderate, dep_major=dep_major, dep_other=dep_other, panic=panic, other_anxiety=other_anxiety,bulimia=bulimia,bin_eat=bin_eat,ptsd=ptsd),list(gender=gender, sexuality=sexuality), mean, na.rm=TRUE))

  gender_sex_filtered <- filter_all(.tbl=gender_sex,.vars_predicate=all_vars(!is.nan(.) & .!=1))

  #write.csv(x=cp_gender_sex_filtered, file="~/mhw_analysis/calpoly_data/cp_gender_sex.csv", row.names=FALSE)
  
  return(list(rg=race_gender, rgf=race_gender_filtered, gs=gender_sex, gsf=gender_sex_filtered))
}
```



```{r}
mhw_results = mhw.results.summarize(data)
mhw_results
```





## Holmes Rahe Analysis
-What things do you want mapped exactly
-end relationship to what
-new roommates to what
```{r}
##Create a new_stress variable 
data = data %>%
  mutate(death_spouse = as.numeric(ifelse(death_spouse=="", 0, 100))) %>%
  mutate(end_relationship = ifelse(end_relationship=="",0, 65)) %>%##################
  mutate(quarentine = ifelse(quarentine=="",0, 65)) %>% ######################
  mutate(death_family = ifelse(death_family=="",0, 63)) %>%
  mutate(injury_ill = ifelse(injury_ill=="",0, 53)) %>%
  mutate(lose_job = ifelse(lose_job=="",0, 47)) %>%
  mutate(family_health_behavior_change = ifelse(family_health_behavior_change=="",0, 44)) %>%
  mutate(sexual_dif = ifelse(sexual_dif=="",0, 39)) %>%
  mutate(new_roommates = ifelse(new_roommates=="",0, 39)) %>%#############
  mutate(finance_change = ifelse(finance_change=="",0, 38)) %>%
  mutate(friend_death = ifelse(friend_death=="",0, 37)) %>%
  mutate(argue_spouse = ifelse(argue_spouse=="",0, 35)) %>%
  mutate(foreclosure = ifelse(foreclosure=="",0, 30)) %>%
  mutate(responsibility_change_work_school = ifelse(responsibility_change_work_school=="",0, 29)) %>%
  mutate(cease_school = ifelse(cease_school=="",0, 26)) %>%
  mutate(living_cond = ifelse(living_cond=="",0, 25)) %>%
  mutate(hours_conditions = ifelse(hours_conditions=="",0, 20)) %>%
  mutate(new_school = ifelse(new_school=="",0, 20)) %>%
  mutate(recreation_change = ifelse(recreation_change=="",0, 19)) %>%
  mutate(church_change = ifelse(church_change=="",0, 19)) %>%
  mutate(social_change = ifelse(social_change=="",0, 18)) %>%
  mutate(take_loan = ifelse(take_loan=="",0, 17)) %>%
  mutate(sleeping_change = ifelse(sleeping_change=="",0, 16)) %>%
  mutate(family_gather_change = ifelse(family_gather_change=="",0, 15)) %>%
  mutate(eating_change = ifelse(eating_change=="",0, 15)) %>% 
  mutate(new_stress = rowSums(.[27:51]))
  
```

### Save the Data
```{r}
write.csv(data, "postCovidDataWScreenings.csv")
```




























