---
title: "PreVsPostCovidAnalysis"
author: "Daniel DeFoe"
date: "8/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```


```{r}
post_df = read.csv("postCovidDataWScreenings.csv") %>%
  mutate(pre_post_covid = "post") %>%
  filter(us_international == "us" & profit_nonprofit == "nonprofit" & twoYear_fourYear == "2") %>%
  select(c("gender", "race", "sexuality", "armed_forces", "parents_edu", "kessler_major", "kessler_moderate", "dep_major", "dep_other", "panic", "other_anxiety", "bulimia", "bin_eat", "ptsd", "pre_post_covid"))

pre_df = read.csv("survey_data_filtered_and_aggregated.csv")%>%
  mutate(pre_post_covid = "pre") %>%
  select(c("gender", "race", "sexuality", "armed_forces", "parents_edu", "kessler_major", "kessler_moderate", "dep_major", "dep_other", "panic", "other_anxiety", "bulimia", "bin_eat", "ptsd", "pre_post_covid"))
```


Combine the datasets of the pre and post covid data, and creating a variable for if there was any there type of depression.

```{r}
both_data = rbind(post_df, pre_df) %>%
  mutate(dep_any = ifelse(dep_major ==1 |dep_other ==1, 1, 0)) %>%
  mutate(kessler_any = ifelse(kessler_major ==1 |kessler_moderate ==1, 1, 0)) %>%
  mutate(anx_any = ifelse(other_anxiety ==1 |panic ==1, 1, 0))
```
## T-tests 
T-tests are conducted to see if there was a significant difference between the number of cases of each of the positive mental health screenings before and after the onset of COVID-19.
```{r}
t.test(dep_major ~ pre_post_covid, data = both_data)
t.test(dep_other ~ pre_post_covid, data = both_data)
t.test(dep_any ~ pre_post_covid, data = both_data)
t.test(kessler_major ~ pre_post_covid, data = both_data)
t.test(kessler_moderate ~ pre_post_covid, data = both_data)
t.test(kessler_any ~ pre_post_covid, data = both_data)
t.test(panic ~ pre_post_covid, data = both_data)
t.test(other_anxiety ~ pre_post_covid, data = both_data)
t.test(anx_any ~ pre_post_covid, data = both_data)
t.test(bulimia ~ pre_post_covid, data = both_data)
t.test(bin_eat ~ pre_post_covid, data = both_data)
t.test(ptsd ~ pre_post_covid, data = both_data)

```


Significant differences between Pre and Post COVID: 
- Dep_major
- Dep_any
- Bullimea --> Almost




```{r}
pre_count = nrow(pre_df)
post_count = nrow(post_df)
both_data2 = both_data %>% 
  select(c(kessler_major, kessler_moderate, kessler_any, dep_major, dep_other, panic, other_anxiety, anx_any, bulimia, bin_eat, ptsd, pre_post_covid)) %>%
  group_by(pre_post_covid) %>%
  summarise_all(list(sum),  na.rm=TRUE) %>% 
  gather(key = "diagnosis", "Proportion", 2:12) %>%
  mutate(Proportion = ifelse(pre_post_covid == "pre", Proportion/pre_count, Proportion/post_count))
head(both_data2)
both_data2$pre_post_covid = relevel(as.factor(both_data2$pre_post_covid), "pre")
ggplot(data = both_data2, aes(x= diagnosis, y = Proportion)) +
  geom_bar(aes(fill = pre_post_covid), position = "dodge", stat="identity") + 
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(title = "Proportion of MH Diagnoses Before and After COVID", x = "Diagnoses", fill= "Pre/Post Covid") 
  
```

The largest differences between pre and post covid is in the number of dep_major cases, with fewer than 10% of respondents screening positive before covid, and almost 30% screening positive after.



